Individual heterogeneity in the functional topography of the DMN in medial prefrontal cortex 

### 2019-02-08 Manuscript.Rmd
Almost done with results draft. Need to add B&B comparison

To establish each subject's network, we selected all the vertices contained within the ROIs (n = 4,801 per subject) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we applied Fisher's r to z transformation, and took the exponential of these values so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05). As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlation values with every other vertex), and $W$ is the adjusted correlation matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. This transormation ensures that every row adds up to zeo. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975]. Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community to be the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects). Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].

@@

To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the clustering derived from the whole subject's data. Given the high degree of overlap across adjacent windows, we attribute a vertex's tendency to persistently shift allegiances to noise. In that regard, and consdiering the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we also examined the relationship between the magnitude of Fiedler vector values with the proportion of times a vertex was part of the DMN community across windows. To do this, we performed a mixed effects logistic regression model, with subject as a mixed effect and vertex-wise eigenmap values (derived from their full dataset) as fixed predictors on the proportion of times each vertex participated in the DMN community. Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time. These thresholds yielded individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.

@@

*NOTE: It might be better to just avoid cluster comparisons at this pre-threshold level*
With these 25 ROIs (23 overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using the whole time series (4800 total TRs from four scanning sessions over two days). Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nVertices` total vertices). After correcting for multiple testing, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas. On average, networks had high densities (i.e. highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`). This degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].

Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning. This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the ROIs. Since this is a data-driven approach, there is no a priori labeling for these communities. We thus defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (7m), and ensured that the binary labeling of the vertices was consistent across subjects. In general, the resulting pattern shows large DMN coverage in PCC, with non-DMN vertices populating its anterior segment. mPFC, on the other hand, is mostly covered by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them. This non-DMN section extends posteriorly onto pregenual cinglate cortex. Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than SV [@Hiser2018].

Before determining the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004]. Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model. Since modularity is agnostic to the desired number of clusters, it was capable of finding more than two communities in our datset. Thus, if both methods agreed in the number and topological organization of the current communities, it would add confidence to our results. We quantified the cross-method agreement with the adjusted rand index (ARI). ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes (e.g. clustered together in partition 1, but separately in 2). This measure has the benefit of being agnostic to labeling schemes, as well as controlling for the expectation that the clusters were randomly produced [@Hubert1985]. This means that positive ARI values compare favorably against chance clustering. Figure 3 shows the distribution of ARI values comparing topologies produced by modularity and spectral partitioning across subjects.

@@

This comparison showed that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`). The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not. This adds evidence to the division of these areas into DMN and non-DMN during rest.

Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was considerable agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`). However, qualitative inspection of the brain community topologies shows good alignment for PCC, with a topologically similar mPFC pattern that shifts topographically across subjects. To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 4). Indeed, this analysis showed that the functional topology of PCC is well maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), while mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) showed significantly lower levels of agreement (paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).

@@

While the distinction of DMN and non-DMN is consistent across session and days, it is possible that the decrease in global ARI values going from full to session-specific data could be due to a dynamic shift in DMN organization. In order to address this possibility, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the original pattern estimated using the whole time series (Figure 9). Note that the length of the windows is well equipped to find stable community features in brain networks [@Gordon2017]. This analysis revealed persistently high levels of agreement for most subjects, with overall low variability (overall mean of each subject's average ARI = `r round(mean(SC_summary$RI), digits = 2)`; SD = `r round(mean(SC_summary$SD), digits = 2)`).

@@

We additionally performed this analysis on mPFC and PCC separately to determine whether these results were region-specific (Figure 10). Even though the within-subject variance remained low for both regions, we found that the average agreement per subject was significantly higher for PCC (paired permutation,*p*= `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`). Nonetheless, the mean ARI across each subject's time series was still relatively high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), thus suggesting that the each individual's DMN distribution is cosiderably stable in time.

We complemented these analyses by asking whether the magnitude of values in the Fiedler vector was associated with the stability of nodes throughout a subject's time series (*PERSONAL NOTE: It might be better to justify this from the use of this vector in statistical mechanics rather than mere curiosity, i.e. extreme FV values are given to elements at the peaks of the wave. Find a simple citation for this.*). Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model, with subject acting as a random effect (Figure 11). The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time. These analysis show that the original pattern identified with the full dataset is temporally stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN vertices in relatively short fMRI sessions (i.e. less than 20 mins).

### *Thresholding*
``` {r Threshold this stupid stuff}
# Get a FV threshold for each subject based on mean vertex stability
# Run the function safely, because some noisy subjects have no relationship between stability and FV
# Note, the mean resulting threshold is similar to the group's 25th and 75th quantiles
TFV <- safely(threshFV)
tempList <- lapply(Summaries, TFV)

# Store thre FV thresholds for all subject 
threshDF <- data_frame(SubjID = substring(subjList,1,6),
                       Lower = NA,
                       Upper = NA)
for (i in seq_along(tempList)) {
  if (is.null(tempList[[i]]$result)) {
    threshDF[i,2:3] <- c(0,0)
  } else {
    threshDF[i,2] <- as.numeric(tempList[[i]]$result[1])
    threshDF[i,3] <- as.numeric(tempList[[i]]$result[2])
  }
}

@@

### *Partition Comparison:Thresholded Full Datasets*
``` {r Partition comparison: all thresholded, echo=FALSE, message = FALSE, cache = TRUE}
# Apply threshold to Summaries
if (threshMaps) {
  for (i in seq(nSubj)) {
  Summaries[[i]] <- Summaries[[i]] %>%
    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
    mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
  }
}

@@

```
### *Partition Comparison: Day 1 vs Day 2*

In order to determine whether the low agreement shown in mPFC across subjects was a function of intrinsic variability or a subject-specific pattern, we compared the agreement among communities estimated with data from each separate day. If the latter were true, within-subject ARI values should be consistently higher than across subjects. Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions. Communities were estimated on concatenated pairs of daily left-right and right-left phase encoded sessions (see Methods for details), and once again compared using ARI. Figure 5 shows pairwise comparisons among ten example subjects for PCC and mPFC separately.

@@

Once again we found greater alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) than mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed higher levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`). However, a coarse comparison of mean ARIs neglects the degree to which subject-wise partitions were indeed idiosyncratic. Therefore, we divided each subject's ARI between days by the ARI values with the days from the other subjects. This ratio denotes the relative specificity of their partition, such that partitions that align well across subjects should yield ratios close to 1, while subject-consistent and unique partitions would produce high ratios. Figure 6 shows the ratios for PCC and mPFC for all subjects. As expected, we found that while both regions had good specificity (i.e. ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PFC), digits = 2)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PCC), digits = 2)`) *CONSIDER IQR INSTEAD OF MEANS/SD* when compared with a paired permutation test (*p* = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`). These test/retest results suggest that the topographic varability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.

### *Partition Comparison: Session*

@@

Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 7), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`). We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 8).

@@

### *Potential Noise Effects (this part is challenging)*

``` {r Noise Effects: tSNR Comparison, echo=FALSE, message = FALSE, cache = TRUE}
## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
# Flexibility vs SNR
# Are vertices with lower SNR switching communities more often?
SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))

# Compare SNR between PCC and mPFC per subject
SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval)
SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff))
prcntSig <- (sum(SNR_PCCvsPFC_perm < 0.05) / nSubj) * 100

# Get the mean SNR for each region and compare overall levels 
SNR_meanPCC <- sapply(tempComm_PCC, function(data) mean(data$varCoeff))
SNR_meanPFC <- sapply(tempComm_PFC, function(data) mean(data$varCoeff))
SNR_meanComp <- list(Values = data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)), SNR = c(SNR_meanPCC, SNR_meanPFC)),
                     Comparison = permute(SNR_meanPCC, SNR_meanPFC)$Pval,
                     ES = cohenD(SNR_meanPCC, SNR_meanPFC))
rm(SNR_meanPCC, SNR_meanPFC)
```

>>>>

All network analyses were performed using the igraph package (CITE) in R 3.4.1. To establish each subject's network, we selected all the vertices contained within the ROIs (n = 4,801 per subject) and computed the Pearson correlation of the time series for every pair of vertices. This produced a weighted network for each subject, where surface vertices were the nodes, and edges the correlations among all of them. Next, we applied Fisher's r to z transformation, and took the exponential of these values so that all weights were positive while maintaining the shape of the original correlation distribution, and retained the edges whose adjusted p-values remained significant after correction for multiple tests (FDR < 0.05). As part of the evaluation step, this procedure (and the community detection outlined below) was applied at four levels: 1) each session separately (1200 TRs each); 2) the concatenated timeseries from each pair of daily sessions (2400 TRs total); 3) each subject's full dataset (4800 TRs total); and 4) on each step of a sliding window analysis (see Partition Evaluation for more details).

@@

Where $I$ is the identity matrix, $D$ is a diagonal matrix containing the strength of each vertex (i.e. the sum of its correlation values with every other vertex), and $W$ is the adjusted correlation matrix. This resulted in a matrix wherein each entry was the normalized value of the connection (from 0 to 1) between any two vertices relative to their combined connectivity strength, and with ones along the diagonal. This transormation ensures that every row adds up to zero. We then computed the eigenvalues and eigenvectors of the normalized Laplacian, and used the eigenvector associated with the second-to-lowest eigenvalue to divide the network into two. This vector (from now on called the 'Fiedler vector') provides a set of positive and negative values to binarize the network with, and guarantees that the resulting communities are connected [@Fiedler1975]. Given that this data-driven method is agnostic to the prevalent function of each community (i.e. DMN or not DMN), we defined the DMN community to be the one containing the DMN-specific area from the meta-analysis (ensuring that the labeling of the DMN community was consistent across subjects). Importantly, given the high density of these networks (see results), spectral partitioning was unlikely to face the issues associated with its use in sparse networks [@Fortunato2016].

@@

To estimate the degree of stability of these partitions per subject we performed a sliding window analysis (20 min windows, 1 min increments, mean number of windows per subject = 37), comparing each window's resulting partition against the clustering derived from the whole subject's data. The length of the windows is well equipped to find stable community features in brain networks [@Gordon2017]. In addition, given the high degree of overlap across adjacent windows, we attribute a vertex's tendency to persistently shift allegiances to noise. In that regard, and consdiering the descriptive relevance of Fiedler eigenvector values in previous fMRI research [@Tian2018], we also examined the relationship between the magnitude of Fiedler vector values with the proportion of times a vertex was part of the DMN community across windows. To do this, we performed a mixed effects logistic regression model, with subject as a mixed effect and vertex-wise eigenmap values (derived from their full dataset) as fixed predictors on the proportion of times each vertex participated in the DMN community. Based on this relationship, we identified a threshold of Fiedler vector values for each subject, such that vertices above these thresholds were persistently associated with either DMN or non-DMN over 95% of the time (all other values were turned into zeros). Individuals without such stable nodes were not thresholded, but their maps were not discarded. Values in the eigenvector maps that did not meet threshold were set to zero, and set to 0.5 during binarization so that they would not bias the mean estimates across subjects. These thresholds yielded individual maps that retained the most stable vertices for further analyses, as well as discarding large sources of noise.

@@

With these 25 ROIs (23 overlapping, 1 DMN-specific, and 1 SV-specific), we estimated each individual's DMN coverage using their full time series (4800 total TRs from four scanning sessions over two days). Each subject's network (n = `r nSubj`) was constructed by performing pairwise correlations among the time series of all the surface vertices contained within the ROIs (`r nVertices` total vertices). After correcting for multiple comparisons, we performed spectral partitioning and modularity on these networks to identify cohesive functional communities denoting DMN and non-DMN areas. On average, networks had high densities (i.e. highly connected) regardless of the amount of data to produce them (mean = `r round(mdAll, digits = 2)`, SD = `r round(sddAll, digits = 3)`). This degree of density is important, as these methods are known to face challenges when computed on sparse networks [@Fortunato2016].

Figure 2 shows a stereotypical subdivision of the ROIs for a single subject (100307) using spectral partitioning. This method dissects a network by the positive and negative values derived from the Fiedler vector (the eigenvector related to the second-to-lowest eigenvalue of the network's Laplacian matrix, see Methods), which we used to binarize the ROIs. Since this is a data-driven approach, there is no a priori labeling for these communities. We thus defined the DMN community as the one containing the one DMN-specific area from the meta-analysis (7m), and ensured that the binary labeling of the vertices was consistent across subjects. In general, the resulting pattern shows large DMN coverage in PCC, with non-DMN vertices populating its anterior segment. On the other hand, mPFC is mostly covered by DMN vertices in its ventral-anterior and dorsal-anterior areas, with a persistent non-DMN pocket between them. This non-DMN section extends posteriorly onto pregenual cinglate cortex (area a24). Interstingly, this topographical combination of dorsal and ventral mPFC, with extensive PCC coverage, matches previous meta-analytic patterns more closely attributed to social cognition than subjective value [@Hiser2018].

Before determining the degree of generazibility of this topological pattern across individuals, we examined the validity of these partitions by comparing them to patterns derived with a modularity algorithm [@Clauset2004]. Modularity seeks to find the pattern of communities that maximizes a quality function that compares the connectivity strength of any two nodes with a null probability model. Since modularity is not bound to a desired number of partitions, it was capable of finding more than two communities in our datset. We quantified the cross-method agreement with the adjusted rand index (ARI). ARI measures the proportion of pairs of nodes in a network that were either clustered together or separately in both partitions, over all possible affiliation changes. This measure has the benefit of being agnostic to labeling schemes, as well as controlling for the expectation that the clusters were randomly produced [@Hubert1985]. This means that positive ARI values compare favorably against chance clustering.

@@

This comparison showed that both clustering methods were in high agreement across subjects (mean = `r round(mean(RI_all_within$Index), digits = 2)` sd = `r round(sd(RI_all_within$Index), digits = 2)`). The importance of this result lies in that while spectral partitioning forces a bipartition of the network, modularity does not. This adds support to the division of these areas into DMN and non-DMN during rest. Since SP and modularity showed converging estimates, from here on we focus on results computed with spectral partitioning to ensure bipartitions.

Next, we examined how similar the partitions were across subjects by computing the ARI between every pair of subjects, and found that there was fairly low agreement overall (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`). However, qualitative inspection of the brain community topologies showed good alignment for PCC, with a topologically similar mPFC pattern that shifted topographically across subjects. To quantify this heterogeneity in mPFC, we performed the same analysis for each region separately (Figure 3). Indeed, this analysis showed that the functional topology of PCC is better maintained across subjects (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`), than mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`)(paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`).

@@

In order to address this the degree of stability of these partitions in time, we performed a sliding window analysis on each subject's full time series (20 min windows shifting at 1 min), comparing the community arrangement derived from each window with the original pattern estimated using the whole time series (Figure 4).

@@

This analysis showed that the mean ARI along each subject's time series was high for both PCC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="PCC"]), digits = 2)`) and mPFC (mean = `r round(mean(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`; SD = `r round(sd(SC_PCCPFC_summary$Index[SC_PCCPFC_summary$Region=="mPFC"]), digits = 2)`), with significantly higher ARI for PCC (paired permutation,*p* = `r SW_PCCvPFC_permuteTest$Pval`; Cohen's D = `r round(SW_PCCvPFC_ES, digits = 2)`). These results suggest that the each individual's DMN distribution is cosiderably stable in time.

There is precedence in thhe literature that the magnitude (and not just the sign) of the Fiedler vector values conveys important information about the role of each node in the network [@Tian2018](**add another citation, like the global map paper**). Therefore, we asked whether the magnitude of these eigenvector values was associated with the stability of nodes in time. Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model (Figure 5). The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time. We refer to this proportion of affiliations over time as the stability of a given node.

``` {r Threshold this stupid stuff}
# Get a FV threshold for each subject based on mean vertex stability
# Run the function safely, because some noisy subjects have no relationship between stability and FV
# Note, the mean resulting threshold is similar to the group's 25th and 75th quantiles
TFV <- safely(threshFV)
tempList <- lapply(Summaries, TFV)

# Store thre FV thresholds for all subject 
threshDF <- data_frame(SubjID = substring(subjList,1,6),
                       Lower = NA,
                       Upper = NA)
for (i in seq_along(tempList)) {
  if (is.null(tempList[[i]]$result)) {
    # if there wass no clear threshold (i.e. noisy participants), then leave it as 0
    threshDF[i,2:3] <- c(0,0)
  } else {
    threshDF[i,2] <- as.numeric(tempList[[i]]$result[1])
    threshDF[i,3] <- as.numeric(tempList[[i]]$result[2])
  }
}

# get descriptives
threshDescriptives <- threshDF %>% 
                        filter(Lower < 0, Upper > 0) %>% 
                        summarize(mL = mean(Lower), 
                                  sdL = sd(Lower), 
                                  mU = mean(Upper), 
                                  sdU = sd(Upper)) %>% 
                        round(., digits = 4)

rm(tempList)

@@

These analyses show that the original pattern identified with the full dataset is stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN and non-DMN vertices, even in relatively short resting fMRI sessions (i.e. less than 20 mins). We therefore thresholded each subject's Fiedler vector to produce these refined maps. We estimated this threshold by selecting the smallest absolute Fiedler vector value that yielded a stability of 95%, for positive (mean = `r threshDescriptives[3]`, SD = `r threshDescriptives[4]`) and negative (mean = `r threshDescriptives[1]`, SD = `r threshDescriptives[2]`) values separately. Vertices that under these thresholds were set to zero (instead of removed) so that the dimensionality of the data was unaffected, and 0.5 in the binarized maps so that they wouldn't bias the calculation of averages. Figure 6 (left) shows the updated partition for the one showed in figure 2. The maps used in all subsequent analyses were thresholded by this individualized criterion.

### *Partition Comparison:Thresholded Full Datasets*
``` {r Partition comparison: all thresholded, echo=FALSE, message = FALSE, cache = TRUE}
# Apply threshold to Summaries
# IMPORTANT: THIS PROCESS OVERWRITES THE VARIABLES FROM THE FIRST COMPARISON SECTION
# THIS IS DONE FOR STORAGE-SAKE, BUT IT MIGHT BE WORTH GIVING THESE TEIR OWN NAME
if (threshMaps) {
  for (i in seq(nSubj)) {
  Summaries[[i]] <- Summaries[[i]] %>%
    mutate(FiedlerVec = ifelse(FiedlerVec > as.numeric(threshDF[i,2]) & FiedlerVec < as.numeric(threshDF[i,3]), 0, FiedlerVec)) %>%
    mutate(FiedlerBinary = ifelse(FiedlerVec > 0, 1, ifelse(FiedlerVec < 0, 0, 0.5)))
  }
}

@@

With these thresholded maps, we recomputed the overall similarity of their functional organization across participants. Compared to before, there was even less overall agreement of the full maps among individuals (mean = `r round(mean(RI_all_between_lowtri), digits = 2)`, SD = `r round(sd(RI_all_between_lowtri), digits = 2)`). The same was true for both PCC (mean = `r round(mean(testPCC), digits = 2)`, SD = `r round(sd(testPCC), digits = 2)`) and mPFC (mean = `r round(mean(testPFC), digits = 2)`, SD = `r round(sd(testPFC), digits = 2)`) separately, although the significance of the differences between these areas was preserved (paired permutation, *p* = `r Overall_PCCvsPFC_permTest$Pval`; Cohen's D = `r round(Overall_PCCvsPFC_ES, digits = 2)`). Figure 6 (right) shows the spatial average of the thresholded binarized partitions across all participants, denoting the proportion of times a vertex was affiliated with the DMN community. This summary conveys a common organizational principle for both communities, but also highlights the considerable variability across individuals in mPFC compared to PCC.

### *Partition Comparison: Day 1 vs Day 2*

The relative high variability seen in the aggregate map could be due to residual noise that was not captured by the sliding window analysis, or variations in the functional organization of mPFC across days. While the sliding window analysis suggested that these partitions are stable, many of the windows contained data from both days. A stricter evaluation of subject-specificity would be to compare every subject's subdivisions produced by data from each day separately. If the variability that we observed was truly due to having captured an individual's unique organization, day to day ARI values should be consistently higher within- than between-subjects. Figure 7 shows pairwise comparisons among ten example subjects for whole brain (left), as well as PCC/mPFC separately (right).

@@

Once again we found low alignment across subjects for PCC (mean = `r round(mean(Halves_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[2]]), digits = 2)`) and mPFC (mean = `r round(mean(Halves_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[2]]), digits = 2)`), but both areas showed relatively high levels of agreement within subjects (PCC: mean = `r round(mean(Halves_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PCCComparison[[1]]), digits = 2)`; mPFC: mean = `r round(mean(Halves_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Halves_PFCComparison[[1]]), digits = 2)`). However, a coarse comparison of mean ARIs neglects the degree to which subject-wise partitions were indeed idiosyncratic. Therefore, we divided everyone's within-subject ARI by the mean ARI of their between-subject comparison. This ratio denotes the relative specificity of their partition, such that partitions that align well across subjects should yield ratios close to 1, while unique and stable partitions would produce high ratios. Figure 8 shows these ARI ratios for PCC and mPFC for all subjects. As expected, we found that while both regions had good specificity (i.e. ratios > 1), the ratios for mPFC (median = `r round(median(Halves_RIRatios_PFC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PFC), digits = 2)`) were significantly higher than those for PCC (median = `r round(median(Halves_RIRatios_PCC), digits = 2)`; SD = `r round(sd(Halves_RIRatios_PCC), digits = 2)`) when compared with a paired permutation test (*p* = `r Halves_mPFCvPCC_permTest$Pval`; Cohen's D = `r round(Halves_mPFCvPCC_ES, digits = 2)`). These test/retest results suggest that the topographic variability seen in mPFC is reliably rooted in subject-specific organization, and not an inability to capture its topology.

### *Partition Comparison: Session based*

@@

Computing SP on networks from individual sessions shows that we can still coarsely capture a subject's unique organizational pattern (Figure 8), even though the overall levels of agreement decreased (PCC between subjects: mean = `r round(mean(Sess_PCCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[2]]), digits = 2)`; PCC within subjects: mean = `r round(mean(Sess_PCCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PCCComparison[[1]]), digits = 2)`); mPFC between subjects: mean = `r round(mean(Sess_PFCComparison[[2]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[2]]), digits = 2)`; mPFC within subjects: mean = `r round(mean(Sess_PFCComparison[[1]]), digits = 2)`, SD = `r round(sd(Sess_PFCComparison[[1]]), digits = 2)`). We again computed each subject's ARI ratio in order to quantify the specificity of these partitions, but this time using the mean ARI acros sessions (Figure 9).

@@

### *Potential Noise Effects*

*NOTE: this part seems less relevant now that we are thresholding the partitions. Might be better to add to sliding window section*

``` {r Noise Effects: tSNR Comparison, echo=FALSE, message = FALSE, cache = TRUE}
## Putative steps to analyze the SNR of the full time series (PCC vs mPFC)
# Flexibility vs SNR
# Are vertices with lower SNR switching communities more often?
# This is pointless if thresholded maps are used, since flexibility is bound to be super low 
SNR_vs_Flex <- sapply(Summaries, function(data) cor(data$varCoeff, data$slideFlexibility))

# Compare SNR between PCC and mPFC per subject after thresholding (this filtering is relevant here because we aren't using ARI anymore)
tempComm_PCC <- lapply(tempComm_PCC, function(data) {data %>% filter(FiedlerVec != 0)})
tempComm_PFC <- lapply(tempComm_PFC, function(data) {data %>% filter(FiedlerVec != 0)}) 
SNR_PCCvsPFC_perm <- sapply(seq_along(tempComm_PCC), function(x) {permute(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)$Pval})
SNR_PCCvsPFC_perm <- p.adjust(SNR_PCCvsPFC_perm, method = "BY")
SNR_PCCvsPFC_ES <- sapply(seq_along(tempComm_PCC), function(x) {cohenD(tempComm_PCC[[x]]$varCoeff, tempComm_PFC[[x]]$varCoeff)})
prcntSig <- mean(SNR_PCCvsPFC_perm < 0.05) * 100

# Get the mean SNR for each region and compare overall levels 
SNR_meanPCC <- sapply(tempComm_PCC, function(data) {mean(data$varCoeff)})
SNR_meanPFC <- sapply(tempComm_PFC, function(data) {mean(data$varCoeff)})
SNR_meanComp <- list(Values = data.frame(Region = c(rep("PCC", nSubj), rep("mPFC", nSubj)), SNR = c(SNR_meanPCC, SNR_meanPFC)),
                     Comparison = permute(SNR_meanPCC, SNR_meanPFC)$Pval,
                     ES = cohenD(SNR_meanPCC, SNR_meanPFC))
rm(SNR_meanPCC, SNR_meanPFC)
```
